International Evaluation of AI Products for Tuberculosis Screening and Precision Diagnosis

### 2020-03-22 SubGroup.Rmd
update

SubgroupTable <- rbind(CAD_Xpert_plot_New, CAD_Xpert_plot_Old, CAD_Xpert_plot_Young, CAD_Xpert_plot_Middle, CAD_Xpert_plot_Senior, CAD_Xpert_plot_Referral, CAD_Xpert_plot_DOTS, CAD_Xpert_plot_WalkIn)
write.csv(SubgroupTable, "Chapter/Subgroup Table/SubgroupTable.csv", row.names = F)
rm(list=(ls()))
```

@@

## New only
l <- ROCPRC(New, New_long)
New <- data.frame(matrix(unlist(l), nrow=5, byrow=T))
New$subgroup <- "New"

## Old only
l <- ROCPRC(Old, Old_long)
Old <- data.frame(matrix(unlist(l), nrow=5, byrow=T))
Old$subgroup <- "Old"

## Young
l <- ROCPRC(Young, Young_long)
Young <- data.frame(matrix(unlist(l), nrow=5, byrow=T))
Young$subgroup <- "Young"

## Middle
l <- ROCPRC(Middle, Middle_long)
Middle <- data.frame(matrix(unlist(l), nrow=5, byrow=T))
Middle$subgroup <- "Middle"

## Senior
l <- ROCPRC(Senior, Senior_long)
Senior <- data.frame(matrix(unlist(l), nrow=5, byrow=T))
Senior$subgroup <- "Senior"

## Referral only
l <- ROCPRC(Referral, Referral_long)
Referral <- data.frame(matrix(unlist(l), nrow=5, byrow=T))
Referral$subgroup <- "Referral"

## DOTS only
l <- ROCPRC(DOTS, DOTS_long)
DOTS <- data.frame(matrix(unlist(l), nrow=5, byrow=T))
DOTS$subgroup <- "DOTS"

@@

aucTable <- rbind(all, New, Old, Young, Middle, Senior, Referral, DOTS, WalkIn)
colnames(aucTable) <- c("DL System", "AUC", "PCAUC", "Subgroup")
write.csv(aucTable, "Results/aucTable.csv")
rm(list=(ls()))

@@

### AUC
age<-ggplot(aucTable[aucTable$Subgroup %in% c("Young", "Middle", "Senior"), ], aes(x=DL.System, y=AUC, fill=Subgroup)) +  geom_bar(stat="identity", width=0.6, position=position_dodge())+theme_minimal()+ theme(legend.position = "top")+  ylim(0, 0.95) + theme(panel.grid.minor = element_line(size=0.5)) + scale_y_continuous(minor_breaks = seq(0 , 0.95, 0.05), breaks = seq(0.65, 0.95, 0.05))

referral<-ggplot(aucTable[aucTable$Subgroup %in% c("Referral", "DOTS", "WalkIn"), ], aes(x=DL.System, y=AUC, fill=Subgroup)) + geom_bar(stat="identity", width=0.7, position=position_dodge())+theme_minimal()+ theme(legend.position = "top")+  ylim(0, 0.95) + theme(panel.grid.minor = element_line(size=0.5)) + scale_y_continuous(minor_breaks = seq(0 , 0.95, 0.05), breaks = seq(0.65, 0.95, 0.05))

history<-ggplot(aucTable[aucTable$Subgroup %in% c("New", "Old"), ], aes(x=DL.System, y=AUC, fill=Subgroup)) + geom_bar(stat="identity", width=0.5, position=position_dodge())+theme_minimal() + theme(legend.position = "top") +  ylim(0, 0.95) + theme(panel.grid.minor = element_line(size=0.5)) + scale_y_continuous(minor_breaks = seq(0 , 0.95, 0.05), breaks = seq(0.65, 0.95, 0.05))

### PRC
agePC<-ggplot(aucTable[aucTable$Subgroup %in% c("Young", "Middle", "Senior"), ], aes(x=DL.System, y=PCAUC, fill=Subgroup)) +  geom_bar(stat="identity", width=0.6, position=position_dodge())+theme_minimal()+ theme(legend.position = "top")+  ylim(0.3, 0.8) + theme(panel.grid.minor = element_line(size=0.5)) + scale_y_continuous(minor_breaks = seq(0 , 0.8, 0.05), breaks = seq(0.3, 0.8, 0.05))

referralPC<-ggplot(aucTable[aucTable$Subgroup %in% c("Referral", "DOTS", "WalkIn"), ], aes(x=DL.System, y=PCAUC, fill=Subgroup)) + geom_bar(stat="identity", width=0.7, position=position_dodge())+theme_minimal()+ theme(legend.position = "top")+  ylim(0.3, 0.8) + theme(panel.grid.minor = element_line(size=0.5)) + scale_y_continuous(minor_breaks = seq(0 , 0.8, 0.05), breaks = seq(0.3, 0.8, 0.05))

historyPC<-ggplot(aucTable[aucTable$Subgroup %in% c("New", "Old"), ], aes(x=DL.System, y=PCAUC, fill=Subgroup)) + geom_bar(stat="identity", width=0.5, position=position_dodge())+theme_minimal() + theme(legend.position = "top") +  ylim(0.3, 0.8) + theme(panel.grid.minor = element_line(size=0.5)) + scale_y_continuous(minor_breaks = seq(0 , 0.8, 0.05), breaks = seq(0.3, 0.8, 0.05))

>>>>

SubgroupTable <- rbind(CAD_Xpert_plot_New, CAD_Xpert_plot_Old, CAD_Xpert_plot_Young, CAD_Xpert_plot_Middle, CAD_Xpert_plot_Senior, CAD_Xpert_plot_Referral, CAD_Xpert_plot_DOTS, CAD_Xpert_plot_WalkIn)
# write.csv(SubgroupTable, "Chapter/Subgroup Table/SubgroupTable.csv", row.names = F)
# rm(list=(ls()))
```

@@

## New only
l <- ROCPRC(New, New_long)
New <- data.frame(matrix(unlist(l), nrow=5, byrow=T))
New$subgroup <- "New cases"

## Old only
l <- ROCPRC(Old, Old_long)
Old <- data.frame(matrix(unlist(l), nrow=5, byrow=T))
Old$subgroup <- "Previously treated cases"

## Young
l <- ROCPRC(Young, Young_long)
Young <- data.frame(matrix(unlist(l), nrow=5, byrow=T))
Young$subgroup <- "Young age"

## Middle
l <- ROCPRC(Middle, Middle_long)
Middle <- data.frame(matrix(unlist(l), nrow=5, byrow=T))
Middle$subgroup <- "Middle age"

## Senior
l <- ROCPRC(Senior, Senior_long)
Senior <- data.frame(matrix(unlist(l), nrow=5, byrow=T))
Senior$subgroup <- "Old age"

## Referral only
l <- ROCPRC(Referral, Referral_long)
Referral <- data.frame(matrix(unlist(l), nrow=5, byrow=T))
Referral$subgroup <- "Referred"

## DOTS only
l <- ROCPRC(DOTS, DOTS_long)
DOTS <- data.frame(matrix(unlist(l), nrow=5, byrow=T))
DOTS$subgroup <- "DOTS retested"

@@

aucTable <- rbind(all, New, Old, Young, Middle, Senior, Referral, DOTS, WalkIn)
colnames(aucTable) <- c("DL System", "AUC", "PCAUC", "Subgroup")
write.csv(aucTable, "Results/aucTable.csv")
# rm(list=(ls()))

@@

### AUC
age<-ggplot(aucTable[aucTable$Subgroup %in% c("Young age", "Middle age", "Old age"), ], aes(x=DL.System, y=AUC, fill=Subgroup)) +  geom_bar(stat="identity", width=0.6, position=position_dodge())+theme_minimal()+ theme(legend.position = "top")+  ylim(0, 0.95) + theme(panel.grid.minor = element_line(size=0.5)) + scale_y_continuous(minor_breaks = seq(0 , 0.95, 0.05), breaks = seq(0.65, 0.95, 0.05))

referral<-ggplot(aucTable[aucTable$Subgroup %in% c("Referred", "DOTS retested", "WalkIn"), ], aes(x=DL.System, y=AUC, fill=Subgroup)) + geom_bar(stat="identity", width=0.7, position=position_dodge())+theme_minimal()+ theme(legend.position = "top")+  ylim(0, 0.95) + theme(panel.grid.minor = element_line(size=0.5)) + scale_y_continuous(minor_breaks = seq(0 , 0.95, 0.05), breaks = seq(0.65, 0.95, 0.05))

history<-ggplot(aucTable[aucTable$Subgroup %in% c("New cases", "Previously treated cases"), ], aes(x=DL.System, y=AUC, fill=Subgroup)) + geom_bar(stat="identity", width=0.5, position=position_dodge())+theme_minimal() + theme(legend.position = "top") +  ylim(0, 0.95) + theme(panel.grid.minor = element_line(size=0.5)) + scale_y_continuous(minor_breaks = seq(0 , 0.95, 0.05), breaks = seq(0.65, 0.95, 0.05))

### PRC
agePC<-ggplot(aucTable[aucTable$Subgroup %in% c("Young age", "Middle age", "Old age"), ], aes(x=DL.System, y=PCAUC, fill=Subgroup)) +  geom_bar(stat="identity", width=0.6, position=position_dodge())+theme_minimal()+ theme(legend.position = "top")+  ylim(0.3, 0.8) + theme(panel.grid.minor = element_line(size=0.5)) + scale_y_continuous(minor_breaks = seq(0 , 0.8, 0.05), breaks = seq(0.3, 0.8, 0.05))

referralPC<-ggplot(aucTable[aucTable$Subgroup %in% c("Referred", "DOTS retested", "WalkIn"), ], aes(x=DL.System, y=PCAUC, fill=Subgroup)) + geom_bar(stat="identity", width=0.7, position=position_dodge())+theme_minimal()+ theme(legend.position = "top")+  ylim(0.3, 0.8) + theme(panel.grid.minor = element_line(size=0.5)) + scale_y_continuous(minor_breaks = seq(0 , 0.8, 0.05), breaks = seq(0.3, 0.8, 0.05))

historyPC<-ggplot(aucTable[aucTable$Subgroup %in% c("New cases", "Previously treated cases"), ], aes(x=DL.System, y=PCAUC, fill=Subgroup)) + geom_bar(stat="identity", width=0.5, position=position_dodge())+theme_minimal() + theme(legend.position = "top") +  ylim(0.3, 0.8) + theme(panel.grid.minor = element_line(size=0.5)) + scale_y_continuous(minor_breaks = seq(0 , 0.8, 0.05), breaks = seq(0.3, 0.8, 0.05))
